An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-11 Manuscript.tex
kable extra is driving me crazy

\emph{Predictors}
\textbf{Venture attention to a resource} A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure (Gebauer, 2009). I use the entrepreneurs' ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources. The GALI questionnaire asks applying entrepreneurs to rank seven acceleration benefits by perceived importance to their ventures. The seven benefits are network development (Network), e.g.~with potential partners and customers, business skill development (Business Skills), mentorship from business experts (Mentorship), indirect funding through access to potential investors/funders (Access to Investors), securing direct venture funding (Direct Funding), gaining access to a group of like-minded entrepreneurs (Access to Like-minded Entrepreneurs), and awareness and credibility (Awareness and Credibility). Setting aside Awareness and Credibility and Access to Like-minded Entrepreneurs, the remaining five benefits can be categorized into three types of resources. Mentorship and Business Skills represent the development of human capital. Network help develop social capital. Direct Funding and Access to Investors improve the financial capital of early-stage ventures directly or indirectly.

@@

\textbf{Institutional level capital} To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI). Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital availability, Financing of Small and Medium Enterprises, Domestic Credit Gaps as different measures of institutional level financial capital. While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).

\emph{Outcomes}
\textbf{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one
if an applicant participate to an accelerator program of choice, and zero otherwise. I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.

\textbf{Resource acquisition} once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention. These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e.~Network) or (c) hiring employees. (a), (b), and (c) are all resource acquisition outcomes.

\textbf{Performance} finaly to measure the impact on venture performance, I use the variable \emph{Revenue} as a proxy for this outcome. This is the most commonly used performance indicator in the management in strategy litrature.

\emph{Control Variables}
\textbf{Human Capital Index} consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience (Colombo \& Grilli, 2005; Dimov \& Shepherd, 2005; Estrin, Mickiewicz, \& Stephan, 2016). I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage). Prior career experience in C-level executive positions (Prior C-level Executive Percentage) is measured by the percentage of founders in the founding teams holding C-level executive positions prior to the current venture. Average Team Tenure measures the average working years of the founding team members. Team Prior Founding measures the number of organizations founded by the founding team before the current venture.

@@

\textbf{Gender composition} the proportion female co-founders in each venture team.

@@

Mixed-effects logit and probit

Given the structure of the data I used a model that incorporates both fixed- and random-effects terms. This helps me take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

@@

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-2.pdf}

\#Attention to capital - venture data

\#\#Control variables

\#\#Constrcuting human capital index (control variable)
\#\#\#Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding

\#\#Gender decomposition variable

\#Reverse code attention variable

\#Distribution of attention

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-2.pdf}

\#\#Outcomes

\#Revenues

\#Human capital acquisition

\#Social capital acquisition

\#Fiancial Capital acquisiton total

\#Predictor and outcome plots
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-2.pdf}

\#Join all 3 datasets

\hypertarget{results}{%
\section{Results}\label{results}}

\#Mixed model analysis - Human capital

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $z$\\
\hline
Intercept & -1.46 & 0.08 & -19.18\\
\hline
Attention to Human capital(AHC) & 0.11 & 0.07 & 1.54\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $z$\\
\hline
Intercept & -0.85 & 0.53 & -1.61\\
\hline
AHC & 0.92 & 0.45 & 2.05\\
\hline
Ease of finding skilled employees & -0.14 & 0.12 & -1.14\\
\hline
AHCxEase of finding skilled employees & -0.17 & 0.10 & -1.79\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $t$\\
\hline
Intercept & 762.25 & 502.25 & 1.52\\
\hline
Attention to Human capital & 2,955.97 & 2,238.11 & 1.32\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $t$\\
\hline
Intercept & -1,955.91 & 3,599.05 & -0.54\\
\hline
AHC & -10,174.65 & 16,704.03 & -0.61\\
\hline
Ease of finding skilled employees & 641.03 & 813.08 & 0.79\\
\hline
AHCxEase of finding skilled employees & 3,118.93 & 3,842.90 & 0.81\\
\hline
\end{tabular}

\#Mixed model analysis - Financial capital

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## participated ~ accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14773.7  14812.1  -7381.8  14763.7    15976 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0388 -0.4890 -0.4207 -0.3515  3.0479 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.300861 0.54851       
##          accel_ben_rank_direct_funding 0.007982 0.08934  -1.00
## Number of obs: 15981, groups:  country, 82
## 
## Fixed effects:
##                               Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                   -1.45326    0.07722 -18.821  < 2e-16 ***
## accel_ben_rank_direct_funding -0.19333    0.06321  -3.059  0.00222 ** 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr)
## accl_bn_r__ -0.171
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ425 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14562.1  14615.8  -7274.1  14548.1    15720 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0463 -0.4908 -0.4210 -0.3513  3.0165 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.287438 0.53613       
##          accel_ben_rank_direct_funding 0.009936 0.09968  -1.00
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                        Estimate Std. Error z value Pr(>|z|)   
## (Intercept)                           -1.349694   0.434021  -3.110  0.00187 **
## accel_ben_rank_direct_funding         -0.210801   0.285396  -0.739  0.46013   
## EOSQ425                               -0.021755   0.112408  -0.194  0.84654   
## accel_ben_rank_direct_funding:EOSQ425  0.003382   0.065751   0.051  0.95898   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ42
## accl_bn_r__ -0.246              
## EOSQ425     -0.983  0.246       
## a____:EOSQ4  0.280 -0.974 -0.289
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ089 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14561.6  14615.2  -7273.8  14547.6    15720 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0482 -0.4904 -0.4209 -0.3510  3.0323 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.284084 0.53299       
##          accel_ben_rank_direct_funding 0.009676 0.09837  -1.00
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                       Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                           -1.21998    0.28033  -4.352 1.35e-05 ***
## accel_ben_rank_direct_funding         -0.24283    0.19650  -1.236    0.217    
## EOSQ089                               -0.07084    0.09006  -0.787    0.432    
## accel_ben_rank_direct_funding:EOSQ089  0.01463    0.05184   0.282    0.778    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ08
## accl_bn_r__ -0.232              
## EOSQ089     -0.960  0.230       
## a____:EOSQ0  0.281 -0.944 -0.300
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: participated ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14561.8  14615.5  -7273.9  14547.8    15720 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0466 -0.4909 -0.4213 -0.3514  3.0629 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.289392 0.53795       
##          accel_ben_rank_direct_funding 0.009926 0.09963  -1.00
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                              Estimate Std. Error z value
## (Intercept)                                -1.3735020  0.1256629 -10.930
## accel_ben_rank_direct_funding              -0.2051438  0.1031016  -1.990
## DOMCREDITGDP                               -0.0010317  0.0017273  -0.597
## accel_ben_rank_direct_funding:DOMCREDITGDP  0.0001439  0.0009667   0.149
##                                            Pr(>|z|)    
## (Intercept)                                  <2e-16 ***
## accel_ben_rank_direct_funding                0.0466 *  
## DOMCREDITGDP                                 0.5503    
## accel_ben_rank_direct_funding:DOMCREDITGDP   0.8817    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ DOMCRE
## accl_bn_r__ -0.193              
## DOMCREDITGD -0.778  0.159       
## a____:DOMCR  0.233 -0.779 -0.313
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ +(accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  541645.1  541683.5 -270817.5  541635.1     15976 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.316  -0.040  -0.029  -0.018 120.803 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr
##  country  (Intercept)                   1.187e+11  344600      
##           accel_ben_rank_direct_funding 2.332e+09   48286  1.00
##  Residual                               3.062e+13 5533830      
## Number of obs: 15981, groups:  country, 82
## 
## Fixed effects:
##             Estimate Std. Error t value
## (Intercept)   226024      79869    2.83
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * EOSQ425 +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  533280.8  533342.1 -266632.4  533264.8     15719 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.311  -0.041  -0.028  -0.016 119.888 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr
##  country  (Intercept)                   1.247e+11  353102      
##           accel_ben_rank_direct_funding 2.606e+09   51053  1.00
##  Residual                               3.109e+13 5575911      
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                       Estimate Std. Error t value
## (Intercept)                              -4885     444377  -0.011
## accel_ben_rank_direct_funding          -191024     590675  -0.323
## EOSQ425                                  59478     112868   0.527
## accel_ben_rank_direct_funding:EOSQ425    31388     134942   0.233
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ42
## accl_bn_r__  0.106              
## EOSQ425     -0.982 -0.103       
## a____:EOSQ4 -0.111 -0.975  0.111
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * EOSQ089 +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  533280.7  533342.0 -266632.3  533264.7     15719 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.310  -0.041  -0.028  -0.015 119.888 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr
##  country  (Intercept)                   1.245e+11  352894      
##           accel_ben_rank_direct_funding 2.412e+09   49109  1.00
##  Residual                               3.109e+13 5575889      
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                       Estimate Std. Error t value
## (Intercept)                              66014     285162   0.231
## accel_ben_rank_direct_funding          -205433     401458  -0.512
## EOSQ089                                  51858      88843   0.584
## accel_ben_rank_direct_funding:EOSQ089    41162     104375   0.394
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ08
## accl_bn_r__  0.083              
## EOSQ089     -0.957 -0.080       
## a____:EOSQ0 -0.094 -0.944  0.098
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

>>>>

\textbf{Predictors}

\emph{Venture attention to a resource} A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure (Gebauer, 2009). I use the entrepreneurs' ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources. The GALI questionnaire asks applying entrepreneurs to rank seven acceleration benefits by perceived importance to their ventures. The seven benefits are network development (Network), e.g.~with potential partners and customers, business skill development (Business Skills), mentorship from business experts (Mentorship), indirect funding through access to potential investors/funders (Access to Investors), securing direct venture funding (Direct Funding), gaining access to a group of like-minded entrepreneurs (Access to Like-minded Entrepreneurs), and awareness and credibility (Awareness and Credibility). Setting aside Awareness and Credibility and Access to Like-minded Entrepreneurs, the remaining five benefits can be categorized into three types of resources. Mentorship and Business Skills represent the development of human capital. Network help develop social capital. Direct Funding and Access to Investors improve the financial capital of early-stage ventures directly or indirectly.

@@

\emph{Institutional level capital} To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI). Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital (VC) availability, Financing of Small and Medium Enterprises (SMEs), Domestic Credit Gaps as different measures of institutional level financial capital. While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).

\textbf{Outcomes}

\emph{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one
if an applicant participate to an accelerator program of choice, and zero otherwise. I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.

\emph{Resource acquisition} once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention. These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e.~Network) or (c) hiring employees. (a), (b), and (c) are all resource acquisition outcomes.

\emph{Performance} finaly to measure the impact on venture performance, I use the variable \emph{Revenue} as a proxy for this outcome. This is the most commonly used performance indicator in the management in strategy litrature.

\textbf{Control Variables}

\emph{Human Capital Index} consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience (Colombo \& Grilli, 2005; Dimov \& Shepherd, 2005; Estrin, Mickiewicz, \& Stephan, 2016). I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage). Prior career experience in C-level executive positions (Prior C-level Executive Percentage) is measured by the percentage of founders in the founding teams holding C-level executive positions prior to the current venture. Average Team Tenure measures the average working years of the founding team members. Team Prior Founding measures the number of organizations founded by the founding team before the current venture.

@@

\emph{Gender composition} the proportion female co-founders in each venture team.

@@

The ventures in our sample are nested within countries. To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource. This helps us account for fixed effects and random effects associated with non-nested grouping factors. Namely, it allows us to take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

The following equation (formulas) show all the models by outcome category. Of note, I run all the following models with conrols and without controls as robustness check. Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e.~female percentage in a team).

\textbf{Resource mobilization}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  \emph{Participated \textasciitilde{} AHC + (AHC \textbar{} Country) ; AHC = Attention to Human Capital}
\item
  \emph{Participated \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
\item
  \emph{Participated \textasciitilde{} AFC + (AFC \textbar{} Country) ; AHC = Attention to Financial Capital}
\item
  \emph{Participated \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
\item
  \emph{Participated \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
\item
  \emph{Participated \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
\item
  \emph{Participated \textasciitilde{} ASC + (ASC \textbar{} Country) ; ASC = Attention to Social Capital}\\
\item
  \emph{Participated \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
\end{enumerate}

\textbf{Resource acquisition}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{8}
\tightlist
\item
  \emph{Total employees \textasciitilde{} AHC + (AHC \textbar{} Country)}
\item
  \emph{Total employees \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC \textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
\item
  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
\item
  \emph{Capital sources \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
\item
  \emph{Capital sources \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
\end{enumerate}

\textbf{Performance}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{16}
\tightlist
\item
  \emph{Revenue \textasciitilde{} AHC + (AHC \textbar{} Country)}
\item
  \emph{Revenue \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC \textbar{} Country)}
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
\item
  \emph{Revenue \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
\end{enumerate}

@@

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-2.pdf}

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-2.pdf}

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-2.pdf}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 1: Effect of attention to human capital}
\centering
\begin{tabular}[t]{lllllllll}
\toprule
\multicolumn{1}{c}{\em{ }} & \multicolumn{4}{c}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
\midrule
Intercept & -1.54 & 0.08 & -19.82 & 0.000 & -1.46 & 0.08 & -19.18 & 0.000\\
Attention to Human capital(AHC) & 0.09 & 0.07 & 1.24 & 0.215 & 0.11 & 0.07 & 1.54 & 0.123\\
\addlinespace[2em]
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hspace{1em}HCI & 0.01 & 0.01 & 1.46 & 0.144 & NA & NA & NA & NA\\
\hspace{1em}GC & 0.24 & 0.06 & 4.17 & 0.000 & NA & NA & NA & NA\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 2: Effect of congruency of venture attention and institutional level of human capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -0.94 & 0.53 & -1.80 & 0.073 & -0.85 & 0.53 & -1.61 & 0.108\\
\hline
AHC & 0.90 & 0.45 & 2.01 & 0.044 & 0.92 & 0.45 & 2.05 & 0.040\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}Ease of finding skilled employees & -0.13 & 0.12 & -1.11 & 0.269 & -0.14 & 0.12 & -1.14 & 0.253\\
\hline
\hspace{1em}AHCxEase of finding skilled employees & 0.01 & 0.01 & 1.37 & 0.171 & -0.17 & 0.10 & -1.79 & 0.074\\
\hline
HCI & 0.24 & 0.06 & 4.06 & 0.000 & NA & NA & NA & NA\\
\hline
GC & -0.17 & 0.10 & -1.80 & 0.073 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 3: Effect of attention to financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -1.53 & 0.08 & -19.55 & 0.000 & -1.45 & 0.08 & -18.82 & 0.000\\
\hline
Attention to Financial capital & -0.19 & 0.06 & -3.02 & 0.003 & -0.19 & 0.06 & -3.06 & 0.002\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.39 & 0.165 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.25 & 0.06 & 4.34 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -1.43 & 0.43 & -3.35 & 0.001 & -1.35 & 0.43 & -3.11 & 0.002\\
\hline
AFC & -0.19 & 0.29 & -0.66 & 0.509 & -0.21 & 0.29 & -0.74 & 0.460\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}Financing of SMEs & -0.02 & 0.11 & -0.20 & 0.845 & -0.02 & 0.11 & -0.19 & 0.847\\
\hline
\hspace{1em}AFCxFinancing of SMEs & 0.01 & 0.01 & 1.30 & 0.193 & 0.00 & 0.07 & 0.05 & 0.959\\
\hline
HCI & 0.25 & 0.06 & 4.25 & 0.000 & NA & NA & NA & NA\\
\hline
GC & 0.00 & 0.07 & -0.02 & 0.988 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -1.31 & 0.28 & -4.74 & 0.000 & -1.22 & 0.28 & -4.35 & 0.000\\
\hline
AFC & -0.23 & 0.20 & -1.17 & 0.244 & -0.24 & 0.20 & -1.24 & 0.217\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}VC Availability & -0.07 & 0.09 & -0.75 & 0.454 & -0.07 & 0.09 & -0.79 & 0.432\\
\hline
\hspace{1em}AFCxVC Availability & 0.01 & 0.01 & 1.31 & 0.190 & 0.01 & 0.05 & 0.28 & 0.778\\
\hline
HCI & 0.24 & 0.06 & 4.23 & 0.000 & NA & NA & NA & NA\\
\hline
GC & 0.01 & 0.05 & 0.22 & 0.824 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -1.46 & 0.13 & -11.62 & 0.000 & -1.37 & 0.13 & -10.93 & 0.000\\
\hline
AFC & -0.20 & 0.10 & -1.91 & 0.056 & -0.21 & 0.10 & -1.99 & 0.047\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}Domestic Credit Gaps & 0.00 & 0.00 & -0.57 & 0.572 & 0.00 & 0.00 & -0.60 & 0.550\\
\hline
\hspace{1em}AFCxDomestic Credit Gaps & 0.01 & 0.01 & 1.30 & 0.192 & 0.00 & 0.00 & 0.15 & 0.882\\
\hline
HCI & 0.25 & 0.06 & 4.24 & 0.000 & NA & NA & NA & NA\\
\hline
GC & 0.00 & 0.00 & 0.08 & 0.938 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 7: Effect of attention to social capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -1.53 & 0.08 & -19.37 & 0.000 & -1.45 & 0.08 & -18.62 & 0.000\\
\hline
Attention to Social capital & 0.12 & 0.07 & 1.79 & 0.073 & 0.11 & 0.07 & 1.69 & 0.091\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}HCI & 0.01 & 0.01 & 1.29 & 0.197 & NA & NA & NA & NA\\
\hline
\hspace{1em}GC & 0.25 & 0.06 & 4.42 & 0.000 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}Table 8: Effect of congruency of venture attention and institutional level of social capital}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
\hline
\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
\cline{2-5} \cline{6-9}
  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
\hline
Intercept & -0.89 & 0.41 & -2.16 & 0.031 & -0.78 & 0.42 & -1.87 & 0.061\\
\hline
ASC & 0.06 & 0.35 & 0.19 & 0.852 & 0.06 & 0.35 & 0.18 & 0.860\\
\hline
\multicolumn{9}{l}{\textbf{Control variables}}\\
\hline
\hspace{1em}State of cluster development & -0.16 & 0.10 & -1.52 & 0.128 & -0.17 & 0.11 & -1.56 & 0.119\\
\hline
\hspace{1em}ASCxState of cluster development & 0.01 & 0.01 & 1.22 & 0.223 & 0.01 & 0.08 & 0.15 & 0.883\\
\hline
HCI & 0.25 & 0.06 & 4.30 & 0.000 & NA & NA & NA & NA\\
\hline
GC & 0.01 & 0.08 & 0.16 & 0.876 & NA & NA & NA & NA\\
\hline
\end{tabular}
\end{table}
